---
title: "Exploratory Analysis"
output: html_document
---

```{r message=FALSE, warning=FALSE, echo=FALSE}
source("analysis.R")
library(ggplot2)
library(dplyr)
```

#### By Daniel Miau, Chloe Lee, Angela Pak, and Trevor Leung (Group 5)

## Distribution Graphs 

```{r distribution, echo=FALSE}
boxplot(state_data$percent_mde,
        main = "Percent of Youths with > 1 MDE",
        xlab = "Percent of Youths",
        horizontal = TRUE)
```

This boxplot shows the distribution of the percantages of youths with at least 
one major depressive episode. On average, states have about 14.20922% of youths 
with at least one MDE, and the interquartile range consists of about 13.2% to 
about 15.2%. The full range goes from 11.40% to 17.57%. This data can be used to 
understand the distribution and average percent of youths with at least one 
MDE in all the states.

```{r distribution2, echo=FALSE}
plot(male_vs_female_count)
```

The number of male mental illness patients under 17 is higher than females by a significant amount. This can lead to a further discussion of factors leading to higher mental health illness patients in males. 

## Relationship Graphs 

```{r coverage_treatment, echo=FALSE}
plot(coverage_vs_treatment)
```
  
In this plot, we compared among states the number of youths whose private
insurance plans did not cover mental or emotional problems to the number of youths
with MDE who did not receive any mental health services. As shown by the scatter plot,
there is a strong positive linear relationship between the two variables,
with a correlation value of 0.9622.

```{r, echo=FALSE}
plot(substance_use_ranking_chart) 
```

In this graph, we compared the percentage of substance use in the top 10 states with the highest percentage of substance use in youths (under age 17). The highest percentage of substance use is from Vermont, while the lowest of the top 10 states is Oregon. 
